\documentclass{article}

\usepackage{calc}
\usepackage{enumitem}
\usepackage[paperwidth=6in, paperheight=9in, margin={1cm,1cm}]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{multicol}
\usepackage{textcomp}
\usepackage[table]{xcolor}

\title{C152 Checklists}
\author{Jared Ledvina}
\date{Sept 2017}

\begin{document}

  \include{common}

  \switchheading{C152 GROUND PROCEDURES}

  \begin{multicols*}{3}

    \flightheading{DISPATCH}

    \begin{clitemize}
      \clitem{Weather}{BRIEF}
      \clitem{NOTAMs}{CHECK}
      \clitem{W\&B}{CHECK}
      \clitem{Perf. Reqs.}{CHECK}
      \clitem{Squawks}{CHECK}
    \end{clitemize}

    \flightheading{PREFLIGHT INSPECTION}

    \begin{clitemize}
      \clitem{Fuel}{DRAIN, CHECK}
      \clitem{AV1ATE}{CHECK}
      \clitem{AROW}{CHECK}
      \clitem{Avionics}{OFF}
      \clitem{Master}{ON}
      \clitem{Fuel Gauge}{TRUE}
      \clitem{Flaps}{EXTEND}
      \clitem{Electrics}{TEST}
      \clitem{Electrics}{OFF}
      \clitem{Master}{OFF}
      \clitem{Oil}{6-8 qts}
      \clitem{Exterior}{CHECK}
      \clitem{Ties/Chocks}{REMOVE}
      \clitem{Baggage}{CHECK}
      \clitem{Walkaround}{EXECUTE}
    \end{clitemize}

    \flightheading{BEFORE START}

    \begin{clitemize}
      \clitem{Preflight}{Complete}
      \clitem{Passengers}{BRIEF}
      \clitem{Seats}{ADJUST}
      \clitem{Seatbelts}{LATCH}
      \clitem{Fuel Selector}{ON}
      \clitem{Mixture}{RICH}
      \clitem{Throttle}{OPEN 1/2"}
      \clitem{Carb Heat}{COLD}
      \clitem{Circuit Breakers}{CHECK}
      \clitem{Electrical Switches}{OFF}
      \clitem{Beacon}{ON}
      \clitem{Avionics}{OFF}
    \end{clitemize}
    
    \flightheading{ENGINE START}

    \begin{clitemize}
      \clitem{Master Switch}{ON}
      \clitem{Prime}{AS REQ'D}
      \clitem{Clear Prop}{ANNOUNCE}
      \clitem{Starter}{ENGAGE}
      \clitem{Throttle}{1000 RPM}
      \clitem{Oil Pressure}{CHECK}
      \clitem{Nav Lights}{AS REQUIRED}
      \clitem{Avionics}{ON}
    \end{clitemize}

    \switchheading{TAXI AWAY FROM HAZARDS}

    \flightheading{AFTER START}

    \begin{clitemize}
      \clitem{Flaps}{RETRACT}
      \clitem{Mixture}{LEAN FOR TAXI}
      \clitem{Radios}{SET}
      \clitem{ATIS}{GET}
      \clitem{Barometer}{SET}
      \clitem{Taxi Diag.}{OPEN}
    \end{clitemize}

    \flightheading{TAXI}

    \begin{clitemize}
      \clitem{Brakes}{TEST}
      \clitem{Controls}{WIND}
      \clitem{Taxi Turns}{EXECUTE}
    \end{clitemize}

    \switchheading{SWITCH TO FLIGHT}

    \flightheading{SHUTDOWN}

    \begin{clitemize}
      \clitem{Brakes}{SET}
      \clitem{Avionics}{OFF}
      \clitem{Electrical}{OFF}
      \clitem{Beacon}{ON}
      \clitem{Throttle}{1000 RPM}
      \clitem{Mixture}{IDLE C/O}
      \clitem{Mags}{OFF}
      \clitem{Master}{OFF}
      \clitem{Control Lock}{INSTALL}
      \clitem{Flight Plan}{CLOSE}
    \end{clitemize}

  \end{multicols*}

  \pagebreak

  \switchheading{C152 FLIGHT PROCEDURES}

  \begin{multicols*}{3}

    \flightheading{TAKEOFF BRIEF}

    \begin{clitemize}
      \clitem{Runway}{CHECK}
      \clitem{HI}{SET TO COMPASS}
      \clitem{Crosswind}{CHECK}
      \clitem{Abort Speed}{NOTE}
      \clitem{Technique}{NOTE}
      \clitem{Flaps}{SET}
      \clitem{Min. Ret. Alt.}{NOTE}
      \clitem{Best Glide}{60-70}
      \clitem{Time}{NOTE}
      \clitem{Mixture}{BEST POWER}
    \end{clitemize}

    \flightheading{BEFORE TAKEOFF}

    \begin{clitemize}
      \clitem{Doors}{CLOSED}
      \clitem{Windows}{LATCHED}
      \clitem{Controls}{CORRECT}
      \clitem{Fuel Selector}{ON}
      \clitem{Trim}{TAKEOFF}
      \clitem{Mixture}{RICH}
      \clitem{Throttle}{1700 RPM}
      \clitem{Carb Heat}{CHECK}
      \clitem{Mags}{CHECK}
      \clitem{Primer}{IN \& LOCKED}
      \clitem{Vaccuum}{CHECK}
      \clitem{Low Vac Light}{OUT}
      \clitem{Low Volt Light}{OUT}
      \clitem{Ammeter}{CHECK}
      \clitem{Voltmeter}{CHECK}
      \clitem{Oil Temp}{CHECK}
      \clitem{Oil Pressure}{CHECK}
      \clitem{Fuel Quantity}{CHECK}
      \clitem{EGT}{CHECK}
      \clitem{Throttle}{Idle 1000 RPM}
      \clitem{Flight Inst.}{CHECK/SET}
      \clitem{Radios}{SET}
      \clitem{Transponder}{SET}
      \clitem{Flaps}{SET}
      \clitem{Strobe}{ON}
      \clitem{Landing Light}{ON}
    \end{clitemize}

    \flightheading{TAKEOFF \& CLIMB}

    \begin{clitemize}
      \clitem{Throttle}{FULL}
      \clitem{Flaps}{UP}
      \clitem{Engine Inst.}{MONITOR}
    \end{clitemize}

    \flightheading{CRUISE}

    \begin{clitemize}
      \clitem{Throttle}{SET}
      \clitem{Mixture}{LEAN}
      \clitem{Trim}{ADJUST}
      \clitem{Engine Instr.}{CHECK}
    \end{clitemize}

    \flightheading{BEFORE LANDING}

    \begin{clitemize}
      \clitem{Fuel Selector}{ON}
      \clitem{ATIS}{GET}
      \clitem{Barometer}{SET}
      \clitem{Tower}{CONTACT}
      \clitem{Mixture}{RICH}
      \clitem{Carb Heat}{AS REQ'D}
      \clitem{Landing Lights}{ON}
      \clitem{Seatbelts}{ADJUST/LOCK}
    \end{clitemize}

    \flightheading{AFTER LANDING}

    \begin{clitemize}
      \clitem{Flaps}{UP}
      \clitem{Mixture}{LEAN}
      \clitem{Carb Heat}{COLD}
      \clitem{Strobe}{OFF}
      \clitem{Nav Lights}{AS REQ'D}
      \clitem{Landing Light}{AS REQ'D}
      \clitem{Radios}{SET}
      \clitem{Taxi Diag.}{OPEN}
    \end{clitemize}

    \switchheading{SWITCH TO GROUND}

    \configheading{TAKEOFF CFGS}

    \configsubheading{NORMAL}

    \begin{clitemize}
      \clitem{Flaps}{UP}
      \clitem{Rotate}{55}
      \clitem{Climb}{74}
    \end{clitemize}

    \configsubheading{SHORT}

    \begin{clitemize}
      \clitem{Flaps}{10}
      \clitem{Brakes}{SET}
      \clitem{Climb}{56 TO 50'}
      \clitem{Flaps}{UP}
    \end{clitemize}

    \configsubheading{SOFT}

    \begin{clitemize}
      \clitem{Flaps}{10}
      \clitem{Nosewheel}{LIGHT}
      \clitem{Ground Effect}{60}
      \clitem{Climb}{65}
      \clitem{Flaps}{UP}
    \end{clitemize}

    \configheading{APPROACH CFGS}

    \configsubheading{NORMAL/SOFT}

    \begin{clitemize}
      \clitem{Flaps}{FULL}
      \clitem{Speed}{65}
    \end{clitemize}

    \configsubheading{SHORT}

    \begin{clitemize}
      \clitem{Flaps}{FULL}
      \clitem{Speed}{60}
    \end{clitemize}

  \end{multicols*}

\end{document}
