\documentclass{article}

\usepackage{calc}
\usepackage{enumitem}
\usepackage{fixltx2e}
\usepackage[paperwidth=6in, paperheight=9in, margin={1cm,1cm}]{geometry}
\usepackage[unicode]{hyperref}
\usepackage[utf8]{inputenc}
\usepackage{multicol}
\usepackage{textcomp}
\usepackage[table]{xcolor}

\title{Citabria 7ECA Checklists}
\author{Jay Vana}
\date{July 2017}

\begin{document}

  \include{common}

  \switchheading{CITABRIA 7ECA GROUND PROCEDURES}

  \begin{multicols*}{3}

    \flightheading{DISPATCH}

    \begin{clitemize}
      \checklistitem{Weather}{BRIEF}
      \checklistitem{NOTAMs}{CHECK}
      \checklistitem{W\&B}{CHECK}
      \checklistitem{Perf. Reqs.}{CHECK}
      \checklistitem{Squawks}{CHECK}
      \checklistitem{Illness}{CHECK}
      \checklistitem{Medication}{CHECK}
      \checklistitem{Stress}{CHECK}
      \checklistitem{Alcohol}{CHECK}
      \checklistitem{Fatigue}{CHECK}
      \checklistitem{Eating}{CHECK}
    \end{clitemize}

    \flightheading{INSPECTION}

    \begin{clitemize}
      \checklistitem{Fuel}{DRAIN, CHECK}
      \checklistitem{AV1ATE}{CHECK}
      \checklistitem{AROW}{CHECK}
      \checklistitem{Mags}{OFF}
      \checklistitem{Fuel Gauges}{TRUE}
      \checklistitem{Fuel Shutoff}{IN}
      \checklistitem{Master}{ON}
      \checklistitem{Lights}{CHECK}
      \checklistitem{Stall Horn}{CHECK}
      \checklistitem{Master}{OFF}
      \checklistitem{ELT}{ARMED}
      \checklistitem{Oil}{6 qts}
      \checklistitem{Exterior}{CHECK}
      \checklistitem{Ties/Chocks}{REMOVE}
      \checklistitem{Walkaround}{EXECUTE}
    \end{clitemize}

    \flightheading{START}

    \begin{clitemize}
      \checklistitem{Passengers}{BRIEF}
      \checklistitem{Seatbelts}{CHECK}
      \checklistitem{Stick}{FULL AFT}
      \checklistitem{Breakers}{CHECK}
      \checklistitem{Fuel Shutoff}{IN}
      \checklistitem{Brakes}{SET}
      \checklistitem{Electrical}{OFF}
      \checklistitem{Door}{CLOSED}
      \checklistitem{Carb. Heat}{OFF}
      \checklistitem{Mixture}{RICH}
    \end{clitemize}

    \flightnote{HOT:\@ SKIP PRIME}

    \begin{clitemize}
      \checklistitem{Prime}{4x}
      \checklistitem{Primer}{LOCKED}
      \checklistitem{Master Switch}{ON}
      \checklistitem{Mags}{ON}
      \checklistitem{Throttle}{SLIGHT}
      \checklistitem{Brakes}{SET}
      \checklistitem{Clear Prop}{ANNOUNCE}
      \checklistitem{Starter}{PUSH}
      \checklistitem{Throttle}{1000 RPM}
      \checklistitem{Oil Pressure}{CHECK}
      \checklistitem{Ammeter}{CHECK}
      \checklistitem{Mixture}{LEAN}
      \checklistitem{Lights}{ON}
      \checklistitem{Radios}{SET}
      \checklistitem{ATIS}{GET}
      \checklistitem{Barometer}{SET}
      \checklistitem{XPDR}{SET}
      \checklistitem{Taxi Diag.}{OPEN}
    \end{clitemize}

    \flightheading{TAXI}

    \begin{clitemize}
      \checklistitem{Brakes}{TEST}
      \checklistitem{Controls}{WIND}
    \end{clitemize}

    \flightheading{RUNUP}

    \begin{clitemize}
      \checklistitem{Brakes}{SET}
      \checklistitem{Controls}{CORRECT}
      \checklistitem{Trim}{TAKEOFF}
      \checklistitem{Flight Inst.}{CHECK}
      \checklistitem{Fuel Shutoff}{IN}
      \checklistitem{Mixture}{BEST POWER}
      \checklistitem{Throttle}{1800 RPM}
      \checklistitem{Mags}{CHECK}
      \checklistitem{Carb. Heat}{CHECK}
      \checklistitem{Engine Inst.}{CHECK}
      \checklistitem{Throttle}{1000 RPM}
      \checklistitem{Doors}{CLOSED}
      \checklistitem{Seatbelts}{CHECK}
    \end{clitemize}

    \switchheading{SWITCH TO FLIGHT}

    \flightheading{SHUTDOWN}

    \begin{clitemize}
      \checklistitem{XPDR}{SET, OFF}
      \checklistitem{Brakes}{SET}
      \checklistitem{Lights}{OFF}
      \checklistitem{GPS}{OFF}
      \checklistitem{Mixture}{IDLE C/O}
      \checklistitem{Mags}{OFF}
      \checklistitem{Master}{OFF}
      \checklistitem{Flight Plan}{CLOSE}
    \end{clitemize}

    \flightheading{SECURING}

    \begin{clitemize}
      \checklistitem{Front Lap Belt}{AROUND STICK}
      \checklistitem{Back Lap Belt}{BUCKLE}
      \checklistitem{Hobbs/Tach}{NOTE}
      \checklistitem{Squawks}{NOTE}
      \checklistitem{Sun Shades}{REPLACE}
      \checklistitem{Wheels}{CHOCK}
      \checklistitem{Tail Wheel}{REORIENT}
      \checklistitem{Ties}{TIE}
      \checklistitem{Doors}{LOCK}
    \end{clitemize}

    \emergencyheading{FIRE ON START}

    \emergencynote{IF START}

    \begin{clitemize}
      \checklistitem{Run}{5 sec}
      \checklistitem{Mixture}{IDLE C/O}
      \checklistitem{Evacuage}{GO}
    \end{clitemize}

    \emergencynote{IF NO START}

    \begin{clitemize}
      \checklistitem{Crank}{CONTINUE}
      \checklistitem{Mixture}{IDLE C/O}
      \checklistitem{Throttle}{FULL}
      \checklistitem{Fuel Shutoff}{OUT}
      \checklistitem{Evacuage}{GO}
    \end{clitemize}

  \end{multicols*}

  \pagebreak

  \switchheading{CITABRIA 7ECA FLIGHT PROCEDURES}

  \begin{multicols*}{3}

    \flightheading{TAKEOFF BRIEF}

    \begin{clitemize}
      \checklistitem{Runway}{CHECK}
      \checklistitem{Crosswind}{CHECK}
      \checklistitem{Abort Speed}{NOTE}
      \checklistitem{Technique}{NOTE}
      \checklistitem{Min. Ret. Alt.}{NOTE}
      \checklistitem{Best Glide}{NOTE}
      \checklistitem{Time}{NOTE}
      \checklistitem{Mixture}{BEST POWER}
    \end{clitemize}

    \flightheading{CLIMB}

    \begin{clitemize}
      \checklistitem{Throttle}{OPEN}
    \end{clitemize}

    \flightnote{IF BELOW 5000}

    \begin{clitemize}
      \checklistitem{Mixture}{BEST POWER}
      \checklistitem{Engine Inst.}{CHECK}
      \checklistitem{Speed}{75-80}
      \checklistitem{Best Rate}{69}
      \checklistitem{Best Angle}{58}
    \end{clitemize}

    \flightheading{PRE-DESCENT}

    \begin{clitemize}
      \checklistitem{Engine Inst.}{CHECK}
      \checklistitem{ATIS}{GET}
      \checklistitem{Barometer}{SET}
      \checklistitem{Tower}{CONTACT}
      \checklistitem{Mixture}{ENRICH}
      \checklistitem{Lights}{ON}
    \end{clitemize}

    \flightheading{AFTER LANDING}

    \begin{clitemize}
      \checklistitem{Trim}{TAKEOFF}
      \checklistitem{Mixture}{LEAN}
      \checklistitem{Taxi Diag.}{OPEN}
      \checklistitem{Carb. Heat}{OFF}
    \end{clitemize}

    \switchheading{SWITCH TO GROUND}

    \configheading{TAKEOFF CFGS}

    \configsubheading{NORMAL}

    \begin{clitemize}
      \checklistitem{Rotate}{55}
      \checklistitem{Climb}{69}
    \end{clitemize}

    \configsubheading{SHORT}

    \begin{clitemize}
      \checklistitem{Rotate}{50}
      \checklistitem{Climb}{58}
    \end{clitemize}

    \configsubheading{SOFT}

    \begin{clitemize}
      \checklistitem{Attitude}{TAIL LOW}
      \checklistitem{After Liftoff}{LEVEL}
      \checklistitem{Climb}{69}
    \end{clitemize}

    \columnbreak

    \configheading{APPROACH CFGS}

    \configsubheading{NORMAL}

    \begin{clitemize}
      \checklistitem{Speed}{60-65}
      \checklistitem{Landing}{FULL STALL}
    \end{clitemize}

    \configsubheading{WHEEL}

    \begin{clitemize}
      \checklistitem{Speed}{65-70}
      \checklistitem{Landing}{MAINS}
      \checklistitem{Stick}{FORWARD}
    \end{clitemize}

    \electricalheading{LOW VOLTAGE}

    \begin{clitemize}
      \checklistitem{Master}{CYCLE}
      \checklistitem{Nonessentials}{OFF}
      \checklistitem{Flight}{TERMINATE}
    \end{clitemize}

    \electricalheading{OVERVOLTAGE}

    \begin{clitemize}
      \checklistitem{Master}{CYCLE}
      \checklistitem{Flight}{TERMINATE}
    \end{clitemize}

    \emergencyheading{ENGINE FAILURE}

    \begin{clitemize}
      \checklistitem{Best Glide}{65}
      \checklistitem{Fuel Shutoff}{ON}
      \checklistitem{Throttle}{HALF}
      \checklistitem{Throttle}{FULL}
      \checklistitem{Mixture}{VARY}
      \checklistitem{Primer}{TRY}
      \checklistitem{Carb. Heat}{ON}
      \checklistitem{Mags}{TEST BOTH}
    \end{clitemize}

    \emergencynote{IF NO RESTART}

    \begin{clitemize}
      \checklistitem{Squawk}{7700}
      \checklistitem{Emergency}{DECLARE}
      \checklistitem{Fuel Shutoff}{OUT}
      \checklistitem{Mixture}{IDLE C/O}
      \checklistitem{Mags}{OFF}
      \checklistitem{Landing}{EXECUTE}
    \end{clitemize}

    \emergencyheading{ENGINE FIRE}

    \begin{clitemize}
      \checklistitem{Mixture}{IDLE C/O}
      \checklistitem{Fuel Shutoff}{OUT}
      \checklistitem{Switches}{ALL OFF}
      \checklistitem{Cabin Heat}{OFF}
      \checklistitem{Extinguisher}{USE}
      \checklistitem{Flight}{TERMINATE}
    \end{clitemize}

    \emergencyheading{ELECTRICAL FIRE}

    \begin{clitemize}
      \checklistitem{Electrical}{OFF}
      \checklistitem{Vents}{OPEN}
      \checklistitem{Extinguisher}{USE}
    \end{clitemize}

    \emergencynote{IF FIRE CONTINUES}

    \begin{clitemize}
      \checklistitem{Flight}{TERMINATE}
    \end{clitemize}

    \columnbreak

    \noteheading

    \begin{itemize}[leftmargin=*]
      \item All airspeeds in MPH
      \item Carb.\ heat always on if icing suspected, indicated by gradual loss of RPM
      \item Only use rudder on takeoff and landing (no brakes)
      \item Mixture should be leaned at any altitude when under 75\% power. Lean until engine roughness, then enrichen to smoothness.
    \end{itemize}

    \configheading{IMPORTANT NUM.}
    \begin{clitemize}
      \clitemsub{V}{rotate}{60}
      \clitemsub{V}{x}{58}
      \clitemsub{V}{y}{75}
      \clitemsub{V}{a}{120}
      \clitemsub{V}{no}{120}
      \clitemsub{V}{ne}{162}
      \checklistitem{Best Glide}{65}
      \checklistitem{Max Gross}{1800}
      \checklistitem{Max Crosswind}{15}
      \checklistitem{Fuel}{35}
    \end{clitemize}

  \end{multicols*}

\end{document}
