\documentclass{article}

\usepackage{calc}
\usepackage{enumitem}
\usepackage[paperwidth=6in, paperheight=9in, margin={1cm,1cm}]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{multicol}
\usepackage{textcomp}
\usepackage[table]{xcolor}

\title{Great Lakes 2T-1A-2 Checklists}
\author{Jay Vana}
\date{August 2017}

\begin{document}

  \include{common}

  \switchheading{GREAT LAKES 2T-1A-2 GROUND PROCEDURES}

  \begin{multicols*}{2}

    \flightheading{DISPATCH}

    \begin{clitemize}
      \checklistitem{Weather}{BRIEF}
      \checklistitem{NOTAMs}{CHECK}
      \checklistitem{W\&B}{CHECK}
      \checklistitem{Perf. Reqs.}{CHECK}
      \checklistitem{Squawks}{CHECK}
    \end{clitemize}

    \flightheading{INSPECTION}

    \begin{clitemize}
      \checklistitem{Fuel}{DRAIN, CHECK}
      \checklistitem{AV1ATE}{CHECK}
      \checklistitem{AROW}{CHECK}
      \checklistitem{Mags}{OFF}
      \checklistitem{Fuel Gauges}{TRUE}
      \checklistitem{Fuel Shutoff}{IN}
      \checklistitem{ELT}{ARMED}
      \checklistitem{Oil}{6-8 QTS}
      \checklistitem{Exterior}{CHECK}
      \checklistitem{Ties/Chocks}{REMOVE}
      \checklistitem{Walkaround}{EXECUTE}
    \end{clitemize}

    \flightheading{START}

    \begin{clitemize}
      \checklistitem{Passengers}{BRIEF}
      \checklistitem{Seatbelts}{SECURE}
      \checklistitem{Master}{BOTH ON}
      \checklistitem{Prop. Control}{FORWARD}
      \checklistitem{Throttle}{SLIGHT}
      \checklistitem{Mixture}{RICH}
      \checklistitem{Brakes}{CHECK}
      \checklistitem{Boost Pump}{AS REQ}
      \checklistitem{Clear Prop.}{ANNOUNCE}
      \checklistitem{Ignition}{START}
      \checklistitem{Oil Pressure}{CHECK}
      \checklistitem{Throttle}{1000 RPM}
      \checklistitem{Radios}{SET}
      \checklistitem{ATIS}{GET}
      \checklistitem{Barometer}{SET}
      \checklistitem{XPDR}{SET}
      \checklistitem{Taxi Diag.}{OPEN}
    \end{clitemize}

    \flightheading{TAXI}

    \begin{clitemize}
      \checklistitem{Brakes}{TEST}
      \checklistitem{Controls}{WIND}
    \end{clitemize}

    \flightheading{RUNUP}

    \begin{clitemize}
      \checklistitem{Brakes}{SET}
      \checklistitem{Controls}{CORRECT}
      \checklistitem{Trim}{TAKEOFF}
      \checklistitem{Stick}{FULL AFT}
      \checklistitem{Flight Inst.}{CHECK}
      \checklistitem{Fuel Shutoff}{IN}
      \checklistitem{Mixture}{BEST POWER}
      \checklistitem{Throttle}{2200 RPM}
      \checklistitem{Mags}{CHECK}
      \checklistitem{Prop. Control}{CYCLE}
      \checklistitem{Prop. Control}{FULL FWD}
      \checklistitem{Engine Inst.}{CHECK}
      \checklistitem{Throttle}{1000 RPM}
      \checklistitem{Seatbelts}{CHECK}
    \end{clitemize}

    \switchheading{SWITCH TO FLIGHT}

    \flightheading{SHUTDOWN}

    \begin{clitemize}
      \checklistitem{XPDR}{SET, OFF}
      \checklistitem{Brakes}{SET}
      \checklistitem{Lights}{OFF}
      \checklistitem{GPS}{OFF}
      \checklistitem{Mixture}{IDLE C/O}
      \checklistitem{Mags}{OFF}
      \checklistitem{Master}{OFF}
      \checklistitem{Flight Plan}{CLOSE}
    \end{clitemize}

    \flightheading{SECURING}

    \begin{clitemize}
      \checklistitem{Front Lap Belt}{AROUND STICK}
      \checklistitem{Back Lap Belt}{BUCKLE}
      \checklistitem{Hobbs/Tach}{NOTE}
      \checklistitem{Squawks}{NOTE}
      \checklistitem{Sun Shades}{REPLACE}
      \checklistitem{Wheels}{CHOCK}
      \checklistitem{Tail Wheel}{REORIENT}
      \checklistitem{Ties}{TIE}
      \checklistitem{Doors}{LOCK}
    \end{clitemize}

  \end{multicols*}

  \pagebreak

  \switchheading{GREAT LAKES 2T-1A-2 FLIGHT PROCEDURES}

  \begin{multicols*}{2}

    \flightheading{TAKEOFF BRIEF}

    \begin{clitemize}
      \checklistitem{Runway}{CHECK}
      \checklistitem{Crosswind}{CHECK}
      \checklistitem{Abort Speed}{NOTE}
      \checklistitem{Technique}{NOTE}
      \checklistitem{Min. Ret. Alt.}{NOTE}
      \checklistitem{Best Glide}{NOTE}
      \checklistitem{Time}{NOTE}
      \checklistitem{Mixture}{BEST POWER}
    \end{clitemize}

    \flightheading{CLIMB}

    \begin{clitemize}
      \checklistitem{Throttle}{OPEN}
      \checklistitem{Mixture}{RICH}
    \end{clitemize}

    \flightheading{PRE-DESCENT}

    \begin{clitemize}
      \checklistitem{Engine Inst.}{CHECK}
      \checklistitem{ATIS}{GET}
      \checklistitem{Barometer}{SET}
      \checklistitem{Tower}{CONTACT}
      \checklistitem{Mixture}{ENRICH}
      \checklistitem{Lights}{ON}
      \checklistitem{Prop. Control}{HIGH RPM}
      \checklistitem{Speed}{75}
    \end{clitemize}

    \flightheading{AFTER LANDING}

    \begin{clitemize}
      \checklistitem{Trim}{TAKEOFF}
      \checklistitem{Mixture}{LEAN}
      \checklistitem{Taxi Diag.}{OPEN}
    \end{clitemize}

    \switchheading{SWITCH TO GROUND}

    \configheading{TAKEOFF CFG}

    \begin{clitemize}
      \checklistitem{Rotate}{55}
      \checklistitem{Climb}{75}
    \end{clitemize}

    \configheading{APPROACH CFG}

    \begin{clitemize}
      \checklistitem{Speed}{75}
      \checklistitem{Landing}{FULL STALL}
    \end{clitemize}

    \columnbreak

    \noteheading

    \begin{itemize}[leftmargin=*]
      \item All airspeeds in MPH
      \item Only use rudder on takeoff and landing (no brakes)
    \end{itemize}

  \end{multicols*}

\end{document}
